Metropolitan Statistical Area Evaluation

### 2022-10-31 src/demo_data_wrangling.Rmd
calculating and adding portland employment data

>>>>

```{r}
# adding portland employment rates from https://data.bls.gov/pdq/SurveyOutputServlet
portland_employment_data <- read_csv(here("data", "raw", "portland_me_employment.csv")) %>% 
  row_to_names(row_number = 10) %>% 
  clean_names() %>% 
  select(year, jan) %>% 
  rename(civilian_labor = jan)

employment_data_jan_2021 <- 100-4.9
employment_data_jan_2022 <- 100- 3.6

yoy <- (employment_data_jan_2022 - employment_data_jan_2021)/ employment_data_jan_2022 *100
